---
title: "Corpula_Celltype"
author: "Taewan Kim"
date: "1/18/2021"
output: html_document
---

# 1. Data Generation

## 1-1. First cell type

```{r}
p <- 8
first_n <- 150
corpula_mean_first <- c(10, 0, 10, 0, 10, 0, 10, 0) # mu
cov_mat_first <- matrix(0, p, p); 
diag(cov_mat_first) <- c(20, 5, 20, 10, 20, 5, 20, 5)
cov_mat_first[1,5] <- 10; cov_mat_first[5,1] <- 10;
cov_mat_first[1,7] <- 10; cov_mat_first[7,1] <- 10;
cov_mat_first[4,5] <- 3; cov_mat_first[5,4] <- 3;
cov_mat_first[4,7] <- 3; cov_mat_first[7,4] <- 3;


norm_first <- MASS::mvrnorm(first_n, corpula_mean_first, cov_mat_first)

corpula_first <- norm_first

# nonparanormal transform
corpula_first <- apply(corpula_first, 2, function(x) {0.4 * sign(x) * abs(x)^1.6})

# this is the gaussian data we need to make nonparanormals
pairs(norm_first, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(corpula_first, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

```

## 1-2. Second cell type

```{r}
second_n <- 200
corpula_mean_second <- c(0, 10, 0, 10,
                         0, 10, 0, 10) # mu

cov_mat_second <- matrix(0, p, p)
diag(cov_mat_second) <- c(5, 20, 5, 10, 5, 20, 5, 20) # Sigma

cov_mat_second[1,5] <- 5; cov_mat_second[5,1] <- 2;
cov_mat_second[1,7] <- 5; cov_mat_second[7,1] <- 2;

norm_second <- MASS::mvrnorm(second_n, corpula_mean_second, cov_mat_second)
corpula_second <- norm_second

# nonparanormal transform
corpula_second <- apply(corpula_second, 2, function(x) {0.4 * sign(x) * abs(x)^1.6})

# this is the gaussian data we need to make nonparanormals
pairs(norm_second, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(corpula_second, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

## 1-3. Third cell type

```{r}
third_n <- 150
corpula_mean_third <- c(10, 0, 0, 10, 
                        8, 8, 10, 10)
cov_mat_third <- matrix(4, p, p);
diag(cov_mat_third) <- c(5, 10, 5, 10, 5, 10, 5, 10) # Sigma

cov_mat_third[4,5] <- 5; cov_mat_third[5,4] <- 5;
#(1,3), (1,5), (1,7), (2,4), (2,6), (2,8), (3,5), (3,7), (4,6), (4,8), (5,7), (6,8)

norm_third <- MASS::mvrnorm(third_n, corpula_mean_third, cov_mat_third)
corpula_third <- norm_third

# nonparanormal transform
corpula_third <- apply(corpula_third, 2, function(x) {0.6 * sign(x) * abs(x)^1.8})

norm_expr <- MASS::mvrnorm(third_n, corpula_mean_third, cov_mat_third)


# this is the gaussian data we need to make nonparanormals
pairs(norm_third, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), upper.panel = NULL)

# this is the nonparanormal 
pairs(corpula_third, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), upper.panel = NULL)
```

## 1-4. Combine the three cell types

```{r}
full_dat <- rbind(cbind(corpula_first, rep(1, first_n)), 
                  cbind(corpula_second, rep(2, second_n)),
                  cbind(corpula_third, rep(3, third_n)))

gen_dat <- full_dat[, 1:8]
gen_label <- full_dat[, 9]

pairs(gen_dat, asp = T, pch = 16,  col = rgb(0.5, 0.5, 0.5, 0.5), lower.panel = NULL)
pairs(gen_dat, asp = T, pch = 16,  col = rgb(0.5, 0.5, 0.5, 0.5), lower.panel = NULL)


```

## 1-5. 2 x 2 Example

```{r}
set.seed(10)
n <- 500
mean_vec_1 <- c(20,0)
cov_mat_1 <- matrix(c(100, 0,
                      0, 50), 2, 2)
####
mean_vec_2 <- c(0,20)
cov_mat_2 <- matrix(c(50, 0,
                      0, 100), 2, 2)

dat_1 <- MASS::mvrnorm(n, mu = mean_vec_1, Sigma = cov_mat_1)

dat_2 <- MASS::mvrnorm(n, mu = mean_vec_2, Sigma = cov_mat_2)

dat <- rbind(dat_1, dat_2)
# dat_3 <- MASS::mvrnorm(n, mu = c(0,0), Sigma = diag(2))
# dat <- rbind(dat_1, dat_2, dat_3)

# par(mar = c(0.5, 0.5, 0.5, 0.5))
plot(dat[,1], dat[,2], asp = T,
     pch = 16, col = rgb(0.5, 0.5, 0.5, 0.1))

dat_1 <- apply(dat_1, 2, function(x){x^2}) # copula-part (monotonic transformation)
dat_2 <- apply(dat_2, 2, function(x){x^2})

dat <- rbind(dat_1, dat_2)

plot(dat[,1], dat[,2], asp = T,
     pch = 16, col = rgb(0.5, 0.5, 0.5, 0.1))

```

# Next Step
# 1. Use a number of correlation methods to find dependencies among the generated data.
# 2. Try to find data that has contrast dependency measures (i.e., high pearson but low distance correlation)
# 3. The goal of simulation is to show that none of the 10 dependency measures aren't perfect; does not answer all. 
# 4. If I cannot find the interesting pattern as I did over the summer,
# 4-1. I could improve on the generated data above by manually chaning the covariance of variables in the mat.
# 4-2. Adding more variables could resolve the issue with some changes. (Mostly L-shaped or one cluster that has no signal)
# 4-3. All three clusters have no signals.
# 4-4. Two of the clusters have no signals, third has a signal but negligible one.
# 5. The number of variables for the final simulation is 20.

# Push more often into the git so that I have a back-up in github.
# Make a function that takes the data and automatically gives the heatmaps of 10 different dependency measures with/without absolute values.

# 2. Dependence Measures

## 2-1.	Pearson’s correlation coefficient (Linearity)

```{r}
cor_pearson_mat <- stats::cor(gen_dat, method = "pearson")

cor_pearson_mat[upper.tri(cor_pearson_mat, diag = T)] <- NA
cor_pearson_mat[1:5,1:5]
```

```{r}
# plot the correlations
cor_pearson_vec <- sort(abs(cor_pearson_mat), decreasing = T)
plot(cor_pearson_vec)
```

## 2-2.	Spearman’s correlation coefficient (Monotone)

```{r}
cor_spearman_mat <- stats::cor(gen_dat, method = "spearman")

cor_spearman_mat[upper.tri(cor_spearman_mat, diag = T)] <- NA
cor_spearman_mat[1:5,1:5]
```

```{r}
# plot the correlations
cor_spearman_vec <- sort(abs(cor_spearman_mat), decreasing = T)
plot(cor_spearman_vec)
```

## 2-3.	Kendall’s correlation coefficient, τ (Monotone)

```{r}
cor_kendall_mat <- stats::cor(gen_dat, method = "kendall")

cor_kendall_mat[upper.tri(cor_kendall_mat, diag = T)] <- NA
cor_kendall_mat[1:5,1:5]
```

```{r}
# plot the correlations
cor_kendall_vec <- sort(abs(cor_kendall_mat), decreasing = T)
plot(cor_kendall_vec)
```

## 2-4.	Distance correlation (Non-linear)

```{r}
library(energy)

cor_dist_mat <- matrix(nrow = ncol(gen_dat), ncol = ncol(gen_dat))

for (i in 2:ncol(gen_dat)){
  for (j in 1:(i-1)){
    cor_dist_mat[i,j] <- dcor2d(as.numeric(gen_dat[, i]), as.numeric(gen_dat[, j]))
  }
}

cor_dist_mat[upper.tri(cor_dist_mat, diag = T)] <- NA
cor_dist_mat[1:5,1:5]
```

```{r}
cor_dist_vec <- sort(abs(cor_dist_mat), decreasing = T)
plot(cor_dist_vec)
```

## 2-5. Hoeffding’s D measure (Distance)

```{r}
library(Hmisc)

hoeff_dist <- hoeffd(x = as.matrix(gen_dat))

cor_hoeffd_mat <- hoeff_dist$D

cor_hoeffd_mat[upper.tri(cor_hoeffd_mat, diag = T)] <- NA
```

```{r}
cor_hoeffd_vec <- sort(abs(cor_hoeffd_mat), decreasing = T)
plot(cor_hoeffd_vec)
```

## 2-6.	Mutual information (MI) (information)

```{r}
library(entropy)

cor_MI_mat <- matrix(nrow = ncol(gen_dat), ncol = ncol(gen_dat))

for (i in 2:ncol(gen_dat)){
  for (j in 1:(i-1)){
    y2d <- discretize2d(as.matrix(gen_dat[, i]),
                        as.matrix(gen_dat[, j]),
                        numBins1 = 20,
                        numBins2 = 20)
    cor_MI_mat[i,j] <- as.numeric(mi.empirical(y2d))
  }
}
```

```{r}
cor_MI_vec <- sort(abs(cor_MI_mat), decreasing = T)
plot(cor_MI_vec)
```

## 2-7. Maximum Information Coefficient (MIC) (information)

```{r}
library(minerva)

cor_MIC <- mine(gen_dat)
cor_MIC_mat <- cor_MIC$MIC

cor_MIC_mat[upper.tri(cor_MIC_mat, diag = T)] <- NA
```

```{r}
cor_MIC_vec <- sort(cor_MIC_mat, decreasing = T)
plot(cor_MIC_vec)
```

## 2-8. Chatterjee's method

```{r}
library(XICOR)

cor_XI_mat <- matrix(nrow = ncol(gen_dat), ncol = ncol(gen_dat))

for (i in 2:ncol(gen_dat)){
  for (j in 1:(i-1)){
    cor_XI_mat[i,j] <- calculateXI(as.numeric(gen_dat[, i]), as.numeric(gen_dat[, j]))
  }
}

cor_XI_mat[upper.tri(cor_XI_mat, diag = T)] <- NA
```

```{r}
cor_XI_vec <- sort(abs(cor_XI_mat), decreasing = T)
plot(cor_XI_vec)
```

## 2-9. Hilbert Schmidt Independence Criterion (HSIC)

- Disregard this coefficient

```{r}
library(dHSIC)

cor_HSIC_mat <- matrix(nrow = ncol(gen_dat), ncol = ncol(gen_dat))

for (i in 2:ncol(gen_dat)){
  for (j in 1:(i-1)){
    cor_HSIC_mat[i,j] <- dhsic(as.numeric(gen_dat[, i]),
                               as.numeric(gen_dat[, j]))$dHSIC
  }
}

cor_HSIC_mat[upper.tri(cor_HSIC_mat, diag = T)] <- NA
```

```{r}
cor_HSIC_vec <- sort(abs(cor_HSIC_mat), decreasing = T)
plot(cor_HSIC_vec)
```

## 2-10. Blomqvist's Beta

```{r}
library(VineCopula)

cor_blomqvist_mat <- BetaMatrix(gen_dat)

cor_blomqvist_mat[upper.tri(cor_blomqvist_mat, diag = T)] <- NA
cor_blomqvist_mat[1:5,1:5]
```

```{r}
cor_blomqvist_vec <- sort(abs(cor_blomqvist_mat), decreasing = T)
plot(cor_blomqvist_vec)
```

# 3. Find contrast characteristics among the correlation coefficients above

## 3-1-1. low pearson (<0.50) and high spearman (>0.5) (linearity vs monotone)

```{r}
cor_contrast1 <- (abs(cor_pearson_mat) < 0.5) & (abs(cor_spearman_mat) > 0.5)
cor_contrast_ind1 <- which(cor_contrast1, arr.ind = T)
nrow(cor_contrast_ind1)
```

## 3-1-2. Visualization of low pearson (<0.50) and high spearman (>0.5) (linearity vs monotone)

```{r}
par(mfrow = c(2, 5))
for (i in 1:nrow(cor_contrast_ind1)){
   index1 <- cor_contrast_ind1[i, 1]; index2 <- cor_contrast_ind1[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"), 
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("Spearman of ", round(cor_spearman_mat[index1, index2], 3))))
}
```

## 3-2-1. high pearson (>0.5) and low spearman (<0.3) (linearity vs monotone)

```{r}
cor_contrast2 <- (abs(cor_pearson_mat) > 0.5) & (abs(cor_spearman_mat) < 0.3)
cor_contrast_ind2 <- which(cor_contrast2, arr.ind = T)
nrow(cor_contrast_ind2)
```

## 3-2-2. Visualization of high pearson (>0.5) and low spearman (<0.3) (linearity vs monotone)

```{r}
par(mfrow = c(2, 5))
for (i in 1:nrow(cor_contrast_ind2)){
   index1 <- cor_contrast_ind2[i, 1]; index2 <- cor_contrast_ind2[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"), 
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("Spearman of ", round(cor_spearman_mat[index1, index2], 3))))
}
```

## 3-3-1. high pearson (>0.50) and low distance correlation (<0.40) (linearity vs Non-linearity)

```{r}
cor_contrast3 <- (abs(cor_pearson_mat) > 0.5) & (abs(cor_dist_mat) < 0.4)
cor_contrast_ind3 <- which(cor_contrast3, arr.ind = T)
nrow(cor_contrast_ind3)
```

## 3-3-2. Visualization of high pearson (>0.70) and low distance correlation (<0.40) (linearity vs Non-linearity)

```{r}
par(mfrow = c(2, 5))

for (i in 1:nrow(cor_contrast_ind3)){
   index1 <- cor_contrast_ind3[i, 1]; index2 <- cor_contrast_ind3[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"), 
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("Dist.Cor of ", round(cor_dist_mat[index1, index2], 3))))
}
```

## 3-4-1. low pearson (<0.40) and high distance correlation (>0.50) (linearity vs Non-linearity)

```{r}
cor_contrast4 <- (abs(cor_pearson_mat) < 0.5) & (abs(cor_dist_mat) > 0.5)
cor_contrast_ind4 <- which(cor_contrast4, arr.ind = T)
nrow(cor_contrast_ind4)
```

## 3-5-1. low pearson (< 0.5) and high MIC (> 0.5) (linearity vs Information)

```{r}
cor_contrast5 <- (abs(cor_pearson_mat) < 0.5) & (abs(cor_MIC_mat) > 0.5)
cor_contrast_ind5 <- which(cor_contrast5, arr.ind = T)
nrow(cor_contrast_ind5)
```

## 3-5-2. Visualization of low pearson (< 0.5) and high MIC (> 0.5) (linearity vs Information)

```{r}
par(mfrow = c(2, 5))

for (i in 1:nrow(cor_contrast_ind5)){
   index1 <- cor_contrast_ind5[i, 1]; index2 <- cor_contrast_ind5[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"), 
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("MIC of ", round(cor_MIC_mat[index1, index2], 3))))
}
```

## 3-6-1. High pearson (> 0.5) and low MIC (< 0.4) (linearity vs Information)

```{r}
cor_contrast6 <- (abs(cor_pearson_mat) > 0.5) & (abs(cor_MIC_mat) < 0.4)
cor_contrast_ind6 <- which(cor_contrast6, arr.ind = T)
nrow(cor_contrast_ind6)
```

## 3-6-2. Visualization of High pearson (> 0.5) and low MIC (< 0.4) (linearity vs Information)

```{r}
par(mfrow = c(2, 5))

for (i in 1:nrow(cor_contrast_ind6)){
   index1 <- cor_contrast_ind6[i, 1]; index2 <- cor_contrast_ind6[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"), 
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("MIC of ", round(cor_MIC_mat[index1, index2], 3))))
}
```
