---
title: "Generating Data"
author: "Taewan Kim"
date: "11/19/2020"
output: html_document
---

```{r}
rm(list=ls())

# import Ziesel dataset and manual data generation functions
source("data_generation.R")
```

```{r}
col; cell_num
head(subset_heatmap[[1]],5)
```
# Check the plot functions

```{r}
exper_n <- 500

par(mfrow = c(2,4))
plot(.generate_lollipop(exper_n),
     main = "Lollipop Shape")
plot(.generate_v(exper_n),
     main = "V Shape")
plot(.generate_local(exper_n),
     main = "Local Correlated Shape")
plot(.generate_quadratic(exper_n),
     main = "Quadratic Shape")
plot(.generate_clusters_L(exper_n),
     main = "L Shape")
plot(.generate_clusters1(exper_n),
     main = "Three Clusters with a line")
plot(.generate_clusters2(exper_n),
     main = "Triangle Shape with a cluster")
```

```{r}
# Method 1.A.I (a "randomized" ordering somewhat)

shuffling_function <- function(vec, window = 5){
  order_vec <- order(vec)
  
  for(i in 1:(length(order_vec)-window)){
    order_vec[i:(i+window)] <- sample(order_vec[i:(i+window)])
  }
  
  order_vec
}

# Method 1.A.II

quadratic_ordering <- function(vec){
  order_vec <- order(vec)
  
  n <- length(order_vec)
  odd_idx <- seq(1, n, by = 2)
  even_idx <- seq(2, n, by = 2)
  
  new_order_vec <- c(order_vec[odd_idx], rev(order_vec[even_idx]))
  new_order_vec
}


dat1_A <- dat
new_order_II_2 <- quadratic_ordering(dat1_A[,2])
dat1_A[,c(2,6)] <- dat1_A[new_order_II_2, c(2,6)]


dat1_B <- dat1_A

new_order1 <- shuffling_function(dat1_B[,1], window = 10)

dat1_B[,c(1,2)] <- dat1_B[new_order1, c(1,2)]

pairs(dat, lower.panel = NULL)
pairs(dat1_A, lower.panel = NULL)
pairs(dat1_B, lower.panel = NULL)
```

# Method 1.B
## All we're going to do is introduce the notion of "cell-types"/"clusters"

```{r}
set.seed(10)
cluster_label <- sample(1:7, 100, replace = T)

dat4 <- dat
for(k in 1:max(cluster_label)){
  idx <- which(cluster_label == k)
  
  dat4[idx,c(1,2)] <- dat4[idx[order(dat4[idx,1])], c(1,2)]
  dat4[idx,c(7,8)] <- dat4[idx[order(dat4[idx,7])], c(7,8)]
}
```

```{r}
variable_transformation <- function(vec1, vec2, mean_val = 0, sd_val = 1){
  val <- stats::pnorm(vec1, mean = mean_val, sd = sd_val)
  
  stats::quantile(vec2, probs = val)
}

set.seed(10)
n <- 1000

dat_test1 <- .generate_lollipop(n)
dat_test2 <- .generate_clusters_L(n)
dat_test3 <- .generate_local(n)
dat_test4 <- .generate_clusters1(n)

expr_dat1 <- cbind(dat_test1, dat_test2, dat_test3, dat_test4)

den_list <- lapply(1:8, function(x){stats::density(expr_dat1[,x])})

mean_vec <- colMeans(expr_dat1); cov_mat1 <- matrix(0.8, 8, 8); diag(cov_mat1) <- 1
# for next, 1. add 0s to the cov_mat

corpula_dat1 <- MASS::mvrnorm(n, mean_vec, cov_mat1)

# nonparanormal transform
corpula_dat1_new <- do.call(cbind, lapply(1:8, function(x){
  variable_transformation(corpula_dat1[,x], expr_dat1[,x], mean_val = mean_vec[x], # for next, 2. use the Ziesel datset (cell_practice) for expr_dat1 part.
                          sd_val = sqrt(diag(cov_mat1)[x]))
}))

# this is the proxy dataset we make to grab monotone functions from
pairs(expr_dat1, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_dat1, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(corpula_dat1_new, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

```{r}
mean_vec <- colMeans(expr_dat1); 

cov_mat2 <- matrix(0.5, 8, 8); diag(cov_mat2) <- 1;
rand_index <- sample(1:8, size = 2, replace = FALSE)
first_ind <- rand_index[1]; second_ind <- rand_index[2];
cov_mat2[2:4,1] <- 0; cov_mat2[1, 2:4] <- 0;

corpula_dat2 <- MASS::mvrnorm(n, mean_vec, cov_mat2)


# nonparanormal transform
corpula_dat2_new <- do.call(cbind, lapply(1:8, function(x){
  variable_transformation(corpula_dat2[,x], expr_dat1[,x], mean_val = mean_vec[x],
                          sd_val = sqrt(diag(cov_mat2)[x]))
}))

# this is the proxy dataset we make to grab monotone functions from
pairs(expr_dat1, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_dat2, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(corpula_dat2_new, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

```

```{r}
mean_vec <- colMeans(expr_dat1); 

cov_mat3 <- matrix(0.9, 8, 8); diag(cov_mat3) <- 1;
rand_index <- sample(1:8, size = 2, replace = FALSE)
first_ind <- rand_index[1]; second_ind <- rand_index[2];
cov_mat3[5:8,1:4] <- 0; cov_mat3[5:8, 1:4] <- 0;
eigen(cov_mat3)

corpula_dat3 <- MASS::mvrnorm(n, mean_vec, cov_mat3)

# nonparanormal transform
corpula_dat3_new <- do.call(cbind, lapply(1:8, function(x){
  variable_transformation(corpula_dat3[,x], expr_dat1[,x], mean_val = mean_vec[x], 
                          sd_val = sqrt(diag(cov_mat3)[x]))
}))

# this is the proxy dataset we make to grab monotone functions from
pairs(expr_dat1, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_dat3, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(corpula_dat3_new, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

# for next, 2. use the Ziesel datset (cell_practice) for expr_dat1 part.

```{r}

first_subset <- subset_data[[1]][, 1:10]
first_n <- nrow(first_subset)
mean_first <- colMeans(first_subset)

cov_mat4 <- matrix(0.8, 10, 10); diag(cov_mat4) <- 1;
#rand_index <- sample(1:8, size = 2, replace = FALSE)
#first_ind <- rand_index[1]; second_ind <- rand_index[2];
#cov_mat3[5:7,3:6] <- 0; cov_mat3[3:6, 5:7] <- 0;

corpula_dat4 <- MASS::mvrnorm(first_n, mean_first, cov_mat4)

# nonparanormal transform
corpula_dat4_new <- do.call(cbind, lapply(1:10, function(x){
  variable_transformation(corpula_dat4[,x], first_subset[,x], mean_val = mean_first[x], 
                          sd_val = sqrt(diag(cov_mat4)[x]))
}))

# this is the proxy dataset we make to grab monotone functions from
pairs(first_subset, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_dat4, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(corpula_dat4_new, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

# Copula with monotone component function

## f(x) = $sign(x)|x|^a$

1. there might be a better way to generate automatically monotonic function that we need (isotonic regression)
2. 

```{r}
set.seed(21)
expr_dat5 <- expr_dat1

n <- nrow(expr_dat5)
mean_vec5 <- colMeans(expr_dat5); 
cov_mat5 <- matrix(0.9, 8, 8); diag(cov_mat5) <- 1;

dat5 <- MASS::mvrnorm(n = n, mu = mean_vec5, Sigma = cov_mat5)

dat5_new <- dat5
for (i in 1:8){
  dat5_new[,i] <- sign(dat5_new[,i])*abs(dat5_new[,i])^0.4  
}

# this is the proxy dataset we make to grab monotone functions from
pairs(expr_dat5, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(dat5, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(dat5_new, asp = T, pch = 16, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

```{r}
second_subset <- subset_data[[1]][, 1:8]
second_n <- nrow(second_subset)
mean_second <- colMeans(second_subset)

covmat_second <- matrix(0.8, 8, 8); diag(covmat_second) <- 1;

corpula_second <- MASS::mvrnorm(second_n, mean_second, covmat_second)

dat_5b <- corpula_second

# nonparanormal transform
for (i in 1:8){
  dat_5b[,i] <- sign(dat_5b[,i])*abs(dat_5b[,i])^0.4  
}

# this is the proxy dataset we make to grab monotone functions from
pairs(second_subset, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_second, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(dat_5b, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

## f(x) = x^3

```{r}
expr_dat6 <- expr_dat1

n <- nrow(expr_dat6)
mean_vec6 <- colMeans(expr_dat6); 
cov_mat6 <- matrix(0.9, 8, 8); diag(cov_mat6) <- 1;

dat6 <- MASS::mvrnorm(n = n, mu = mean_vec6, Sigma = cov_mat6)

dat6_new <- dat6

for (i in 1:8){
  dat6_new[,i] <- dat6_new[,i]^3
}

# this is the proxy dataset we make to grab monotone functions from
pairs(expr_dat6, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(dat6, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(dat6_new, asp = T, pch = 16, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

```{r}
third_subset <- subset_data[[1]][, 1:8]
third_n <- nrow(third_subset)
mean_third <- colMeans(third_subset) # mu

covmat_third <- matrix(0.8, 8, 8); diag(covmat_third) <- 1; # Sigma

corpula_third <- MASS::mvrnorm(third_n, mean_third, covmat_third)

dat_5c <- corpula_third

# nonparanormal transform
for (i in 1:8){
  dat_5c[,i] <- dat_5c[,i]^3  # f
}

# this is the proxy dataset we make to grab monotone functions from
pairs(third_subset, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_third, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(dat_5c, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

1. generate datasets strictly independent or dependent  
2. celltype:3 (do simulation datasets three different times), column: 8
3. 500

```{r}
new_dat <- data.frame()
p <- 8
row_num <- c(150, 150, 200)

# for 3 Cell_type
for (i in 1:3){
  
  dat_list <- lapply(1:(p/2), function(round){
    k <- sample(1:3, 1)
    if (k == 1) {
      cur_dat <- .generate_pos_linear(row_num[i])
    } else if (k == 2){
      cur_dat <- .generate_neg_linear(row_num[i])
    } else {
      cur_dat <- .generate_independent(row_num[i])
    }
  })
 
  dat_list <- lapply(dat_list, function(dat){
     dat[order(dat[,1]),]  
   })
  
  # concatenate column-wise
  new_dat <- rbind(new_dat, do.call(cbind, dat_list))
}

plot(new_dat)

plot(new_dat[,c(1,8)])
```

```{r}
cor_pearson_mat <- stats::cor(new_dat, method = "pearson")

cor_pearson_mat[upper.tri(cor_pearson_mat, diag = T)] <- NA
cor_pearson_mat[1:5,1:5]
```

```{r}
new_nrow <- nrow(new_dat)
new_mean <- colMeans(new_dat)

covmat_new <- matrix(0.8, 8, 8); diag(covmat_new) <- 1;

corpula_new <- MASS::mvrnorm(new_nrow, new_mean, covmat_new)

dat_cor_new <- corpula_new

# nonparanormal transform
for (i in 1:8){
  dat_cor_new[,i] <- sign(dat_cor_new[,i])*abs(dat_cor_new[,i])^0.4  
}

# this is the proxy dataset we make to grab monotone functions from
pairs(new_dat, asp = T, col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the gaussian data we need to make nonparanormals
pairs(corpula_new, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

# this is the nonparanormal 
pairs(dat_cor_new, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)

```
