---
title: "Lollipop2"
author: "Taewan Kim"
date: "5/26/2021"
output:
    html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
---

# 1. Data Generation

## 1-1. First cell type

```{r}

p <- 10
first_n <- 200
copula_mean_first <- c(0, 0, 0, 0, 0,
                       0, 0, 0, 0, 0) # mu
cov_mat_first <- matrix(0, p, p); 
diag(cov_mat_first) <- c(3, 3, 2.5, 3.8, 3,
                         3, 4, 3.5, 3, 2.8)

set.seed(10)
norm_first <- MASS::mvrnorm(first_n, copula_mean_first, cov_mat_first)
copula_first <- norm_first
# nonparanormal transform
copula_first <- apply(copula_first, 2, function(x) {0.4 * sign(x) * abs(x)^1.6})
# this is the gaussian data we need to make nonparanormals
pairs(norm_first, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
# this is the nonparanormal 
pairs(copula_first, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```

## 1-2. second cell type

```{r}
second_n <- 250
copula_mean_second <- c(2.5, 2.5, 2.5, 2.1, 2.5, 
                       2.3, 2, 2.4, 2.6, 2.5)
cov_mat_second <- matrix(2, p, p);
diag(cov_mat_second) <- c(2.5, 2.4, 2.5, 2.5, 2.6,
                          2.3, 2.5, 2.5, 2.2, 2.3) # Sigma

set.seed(10)
norm_second <- MASS::mvrnorm(second_n, copula_mean_second, cov_mat_second)
copula_second <- norm_second
# nonparanormal transform
copula_second <- apply(copula_second, 2, function(x) {0.6 * sign(x) * abs(x)^1.4})
norm_expr <- MASS::mvrnorm(second_n, copula_mean_second, cov_mat_second)
# this is the gaussian data we need to make nonparanormals
pairs(norm_second, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
# this is the nonparanormal 
pairs(copula_second, asp = T, pch = 16,  col = rgb(0.5,0.5,0.5,0.5), lower.panel = NULL)
```


## 1-3. Combine the two cell types

```{r}
full_dat <- rbind(cbind(copula_first, rep(1, first_n)), 
                 cbind(copula_second, rep(2, second_n)))

gen_dat <- full_dat[, 1:10]
gen_label <- full_dat[, 11]

pairs(gen_dat, asp = T, pch = 16,  col = gen_label, lower.panel = NULL)
pairs(gen_dat, asp = T, pch = 16,  col = rgb(0.5, 0.5, 0.5, 0.5), lower.panel = NULL)
```

```{r}
plot(gen_dat[, 4], gen_dat[, 9])
```


## 1-4. Defining functions for next section

- Define functions that calculate correlation matrices and draw heatmaps of corresponding matrices

```{r}
library(reshape2) # melt function
library(ggplot2) # ggplot function
library(pcaPP) # Fast Kendall function
library(energy) # Distance Correlation
library(Hmisc) # Hoeffding's D measure
library(zebu) # Normalized Mutual Information
# library(minerva) # Maximum Information Coefficient
library(XICOR) # Chatterjee's Coefficient
# library(dHSIC) # Hilbert Schmidt Independence Criterion
library(VineCopula) # Blomqvist's Beta

make_cormat <- function(dat_mat){
dat_mat <- gen_dat
matrix_dat <- matrix(nrow = ncol(dat_mat), ncol = ncol(dat_mat))
  cor_mat_list <- list()
  
  basic_cor <- c("pearson", "spearman")
  # find each of the correlation matrices with Pearson, Spearman, Kendall Correlation Coefficients
  for (i in 1:2){
    cor_mat <- stats::cor(dat_mat, method = basic_cor[i])
    cor_mat[upper.tri(cor_mat, diag = T)] <- NA
    cor_mat_list[[i]] <- cor_mat
  }
  
  # functions that take matrix or data.frame as input
  no_loop_function <- c(pcaPP::cor.fk, Hmisc::hoeffd, 
                        VineCopula::BetaMatrix)
  for (i in 3:5){
    fun <- no_loop_function[[i-2]]
    cor_mat <- fun(dat_mat)
    if (i == 4){ # Hoeffding's D
      cor_mat <- cor_mat$D
    }
    cor_mat[upper.tri(cor_mat, diag = T)] <- NA
    cor_mat_list[[i]] <- cor_mat
  }
  
  # functions that take two variables as input to calculate correlations.
  need_loop <- c(zebu::lassie, energy::dcor2d, XICOR::calculateXI)

  for (i in 6:8){
    
    fun <- need_loop[[i-5]]
    
    cor_mat <- matrix(nrow = ncol(dat_mat),
                      ncol = ncol(dat_mat))
    
    for (j in 2:ncol(dat_mat)){
      for (k in 1:(j-1)){
        if (i == 6){
          cor_mat[j, k] <- fun(cbind(dat_mat[, j], dat_mat[, k]), continuous=c(1,2), breaks = 6, measure = "npmi")$global

        } else {
          cor_mat[j, k] <- fun(as.numeric(dat_mat[, j]),
                               as.numeric(dat_mat[, k]))
        }
      }
    }
    
    cor_mat[upper.tri(cor_mat, diag = T)] <- NA
    cor_mat_list[[i]] <- cor_mat
  }
  return(cor_mat_list)
}

draw_heatmap <- function(cor_mat){
    len <- 8
    melted_cormat <- melt(cor_mat)
    melted_cormat <- melted_cormat[!is.na(melted_cormat$value),]
    break_vec <- round(as.numeric(quantile(melted_cormat$value,
                                           probs = seq(0, 1, length.out = len),
                                           na.rm = T)),
                       4)
    break_vec[1] <- break_vec[1]-1
    break_vec[len] <- break_vec[len]+1
    melted_cormat$value <- cut(melted_cormat$value, breaks = break_vec)
    heatmap_color <- unique(melted_cormat$value)
  
    heatmap <- ggplot(data = melted_cormat, aes(x = Var2, y = Var1, fill = value))+
      geom_tile(colour = "Black") +
      ggplot2::scale_fill_manual(breaks = sort(heatmap_color), 
                                 values = rev(scales::viridis_pal(begin = 0, end = 1)
                                              (length(heatmap_color)))) +
      theme_bw() + # make the background white
      theme(panel.border = element_blank(), panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), axis.ticks = element_blank(),
            # erase tick marks and labels
            axis.text.x = element_blank(), axis.text.y = element_blank())
    
    return (heatmap)
}

make_cor_heatmap <- function(dat_mat){
  fun_lable <- c("Pearson's Correlation", "Spearman's Correlation", "Kendall's Correlation",
                 "Hoeffding's D", "Blomqvist's Beta", "NMI", 
                 "Distance Correlation", "XI Correlation")
  
  cor_heatmap_list <- list()
  cor_abs_heatmap_list <- list()
  
  # make correlation matrices
  cor_mat_list <- make_cormat(dat_mat)
  
  for (i in 1:8){
    cor_mat <- cor_mat_list[[i]]
    
    # get heatmaps
    cor_heatmap <- draw_heatmap(cor_mat)
    
    # ggplot labels
    ggplot_labs <- labs(title = paste("Heatmap of", fun_lable[i]),
                      x = "",
                      y = "",
                      fill = "Coefficient") # change the title and legend label
      
    cor_heatmap_list[[i]] <- cor_heatmap + ggplot_labs
    
    if (i %in% c(1,2,3,4,6)){
      cor_abs_mat <- abs(cor_mat_list[[i]])
      cor_abs_heatmap <- draw_heatmap(cor_abs_mat)
      ggplot_abs_labs <- labs(title = paste("Abs Heatmap of", fun_lable[i]),
                              x = "", # change the title and legend label
                              y = "", 
                              fill = "Coefficient") 
      cor_abs_heatmap_list[[i]] <- cor_abs_heatmap + ggplot_abs_labs
    } else {
      ggplot_abs_labs <- labs(title = paste("Abs Heatmap of", fun_lable[i]),
                              subtitle = "Equivalent to Non-Abs Heatmap",
                              x = "", # change the title and legend label
                              y = "", 
                              fill = "Coefficient") 
      cor_abs_heatmap_list[[i]] <- cor_heatmap + ggplot_abs_labs
    }
  }
  
  ans <- list(cor_heatmap_list, cor_abs_heatmap_list)
  
  return (ans)
}
```


```{r}
lst <- make_cor_heatmap(gen_dat)
cormat_list <- make_cormat(gen_dat)

# lst[[1]]
lst[[1]][[4]]

cor_pearson_mat <- cormat_list[[1]]; cor_spearman_mat <- cormat_list[[2]];
cor_kendall_mat <- cormat_list[[3]]; cor_hoeffd_mat <- cormat_list[[4]];
cor_blomqvist_mat <- cormat_list[[5]]; cor_dist_mat <- cormat_list[[6]];
cor_MI_mat <- cormat_list[[7]]; cor_XI_mat <- cormat_list[[8]];
```


## 3-1. Find contrast characteristics among the correlation coefficients above

## 3-1-1. high pearson (> 0.70) and low distance correlation (< 0.35) (linearity vs Non-linearity)

```{r}
cor_contrast1 <- (abs(cor_pearson_mat) > 0.70) & (abs(cor_dist_mat) < 0.35)
cor_contrast_ind1 <- which(cor_contrast1, arr.ind = T)
nrow(cor_contrast_ind1)
```

## 3-1-2. Visualization of high pearson (> 0.70) and low distance correlation (< 0.35) (linearity vs Non-linearity)

```{r}
par(mfrow = c(2, 4))

for (i in 1:nrow(cor_contrast_ind1)){
   index1 <- cor_contrast_ind1[i, 1]; index2 <- cor_contrast_ind1[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"),
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("Dist.Cor of ", round(cor_dist_mat[index1, index2], 3))))
}
```

## 3-2-1. High Pearson (> 0.7) and low XI (< 0.35) (linearity vs distance)

```{r}
cor_contrast2 <- (abs(cor_pearson_mat) > 0.7) & (abs(cor_XI_mat) < 0.35)
cor_contrast_ind2 <- which(cor_contrast2, arr.ind = T)
nrow(cor_contrast_ind2)
```

## 3-2-2. Visualization of high Pearson (> 0.7) and low XI (< 0.35) (linearity vs distance)

```{r}
par(mfrow = c(2, 3))

for (i in 1:nrow(cor_contrast_ind2)){
   index1 <- cor_contrast_ind2[i, 1]; index2 <- cor_contrast_ind2[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"),
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("XI of ", round(cor_XI_mat[index1, index2], 3))))
}
```

## 3-3-1. High Pearson (> 0.7) and low Blomqvist's beta (< 0.45) (linearity vs monotone)

```{r}
cor_contrast3 <- (abs(cor_pearson_mat) > 0.7) & (abs(cor_blomqvist_mat) < 0.45)
cor_contrast_ind3 <- which(cor_contrast3, arr.ind = T)
nrow(cor_contrast_ind3)
```

## 3-3-2. Visualization of High Pearson (> 0.7) and low Blomqvist's beta (< 0.45) (linearity vs monotone)

```{r}
par(mfrow = c(2, 3))

for (i in 1:nrow(cor_contrast_ind3)){
   index1 <- cor_contrast_ind3[i, 1]; index2 <- cor_contrast_ind3[i, 2]
   plot(gen_dat[,index1], gen_dat[,index2], col = gen_label, asp = T,
      pch = 16, xlab = paste0(colnames(gen_dat)[index1], ", (", index1, ")"),
      ylab = paste0(colnames(gen_dat)[index2], ", (", index2, ")"),
      main = paste(paste0("Pearson of ", round(cor_pearson_mat[index1, index2], 3)),
                   "\n",
                   paste0("Beta of ", round(cor_blomqvist_mat[index1, index2], 3))))
}
```
