---
title: "Untitled"
author: "Taewan Kim"
date: "6/28/2021"
output: html_document
---
# Data Import

## Import dataset

```{r}
library(reshape2) # melt function
library(ggplot2) # ggplot function
library(pcaPP) # Fast Kendall function
library(energy) # Distance Correlation
library(Hmisc) # Hoeffding's D measure
library(zebu) # Normalized Mutual Information
# library(minerva) # Maximum Information Coefficient
library(XICOR) # Chatterjee's Coefficient
# library(dHSIC) # Hilbert Schmidt Independence Criterion
library(VineCopula) # Blomqvist's Beta
```

```{r, cache=TRUE}
# Import Ziesel dataset
dat <- read.csv("Zeisel_preprocessed.csv", row.names = 1)
cell_type <- read.table("Zeisel_cell_info.txt", sep = "\t", header = 1)

# Get the labels for each cell
cluster_labels <- as.numeric(as.factor(cell_type$level1class))
```

```{r}
cell_labels <- unique(cell_type$level1class)
rand_ind <- c()

for (cell in cell_labels){
  set.seed(10)
  subcell_ind <- which(cell_type$level1class == cell)
  sub_rand <- sample(length(subcell_ind),
                     length(subcell_ind)/10)
  rand_ind <- c(rand_ind, subcell_ind[sub_rand])
}

dat_hclust <- hclust(dist(t(dat)))
dat_index <- dat_hclust$order


sub_dat <- dat[rand_ind, dat_index]
# dim

sub_celltype <- cell_type[rand_ind, ]
sub_cluster_labels <- as.numeric(as.factor(sub_celltype$level1class))
```

```{r}
dim(sub_dat)
```

# Dependence Measures

## 1.	Pearson’s correlation coefficient

- it measures the linear dependence.
- the runtime is very short compared to other methods.

```{r}
a <- Sys.time()
cor_pearson_mat <- stats::cor(sub_dat, method = "pearson")
b <- Sys.time()

b-a
```

## 2.	Spearman’s correlation coefficient

- captures monotonous relationship within data.
- the runtime is very short compared to other methods.

```{r}
a <- Sys.time()
cor_spearman_mat <- stats::cor(sub_dat, method = "spearman")
b <- Sys.time()
b-a
```

## 3. Faster Kendall's tau (pcaPP)

```{r}
a <- Sys.time()
faster_kendall_mat <- cor.fk(sub_dat)
b <- Sys.time()
b - a
```

Sys.time()


## 4.	Distance correlation

- it is a fully non-parametric measure that identifies non-linear relationships between two random variables with energy distances

```{r}
library(energy)
a <- Sys.time()
cor_dist_mat <- matrix(nrow = ncol(sub_dat), ncol = ncol(sub_dat))

for (i in 2:ncol(sub_dat)){
  for (j in 1:(i-1)){
    cor_dist_mat[i,j] <- dcor2d(as.numeric(sub_dat[, i]), as.numeric(sub_dat[, j]))
  }
}

b <- Sys.time()
b - a
```

## 5. Hoeffding’s D measure

- tests the independence of the data sets by calculating the distance between the product of the marginal distributions

```{r}
a <- Sys.time()
hoeff_dist <- hoeffd(x = as.matrix(sub_dat))
cor_hoeffd_mat <- hoeff_dist$D
b <- Sys.time()

b - a
```

## 6.	Normalized Mutual Information (MI)

- measures how much one random variable tells us about another.

```{r}
a <- Sys.time()
cor_NMI_mat <- matrix(nrow = ncol(sub_dat), ncol = ncol(sub_dat))
for (j in 2:ncol(cor_NMI_mat)){
  for (k in 1:(j-1)){
    cor_NMI_mat[j, k] <- zebu::lassie(cbind(sub_dat[, j], sub_dat[, k]), continuous=c(1,2), breaks = 6, measure = "npmi")$global
  }
}
b <- Sys.time()

b - a
```

## 7. Chatterjee's method

```{r}
a <- Sys.time()

cor_XI_mat <- matrix(nrow = ncol(sub_dat), ncol = ncol(sub_dat))

for (i in 2:ncol(sub_dat)){
  for (j in 1:(i-1)){
    cor_XI_mat[i,j] <- calculateXI(as.numeric(sub_dat[, i]), as.numeric(sub_dat[, j]))
  }
}
b <- Sys.time()

b - a
```

## 8. Blomqvist's Beta

```{r}
a <- Sys.time()
cor_blomqvist_mat <- BetaMatrix(sub_dat)
b <- Sys.time()

b - a
```