---
title: "cluster_practice"
author: "Taewan Kim"
date: "8/18/2020"
output: html_document
---

# Data Import

## Import dataset

```{r}
# Import Ziesel dataset
dat <- read.csv("~/Box Sync/Zeisel_preprocessed.csv", row.names = 1)
cell_type <- read.table("~/Box Sync/Zeisel_cell_info.txt", sep = "\t", header = 1)

# Get the labels for each cell
cluster_labels <- as.numeric(as.factor(cell_type$level1class))
cell_label <- unique(cell_type$level1class)
```

```{r}
# Randomly select a pair from the columns
set.seed(10)
rand_ind <- sample(seq(1, ncol(dat), by = 1), size = 2, replace = F)

# Assign variables for the later
col <- ncol(dat)
ind1 <- rand_ind[1]; ind2 <- rand_ind[2]
sub_dat <- dat[, c(ind1, ind2)]
cell_num <- length(unique(cluster_labels))

# the plot that the picked pair looks like
plot(dat[,ind1], dat[,ind2], 
     col = cluster_labels, asp = T, pch = 16,
     xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
     ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"), )
```

# Clustering Method (7c2 Combinations)

## Method 1 : P-values in Two-sample Tests

```{r}
t_matrix <- matrix(data = NA, nrow = cell_num, ncol = cell_num)

# Conduct the t.test for 7C2 times 
for (i in 2:cell_num){
  for (j in 1:(i-1)){
    if (i == j) {next}
    x <- sub_dat[which(cluster_labels == i), ]
    y <- sub_dat[which(cluster_labels == j), ]
    
    ttest_xy <- stats::t.test(x, y, alternative = "two.sided")
    t_matrix[i,j] <- ttest_xy$p.value
  }
}

```

```{r}
par(mfrow = c(3,4))
for (i in 2:cell_num){
  for (j in 1:(i-1)){
    tmp <- which(cluster_labels %in% c(i,j))
    sub_dat2 <- sub_dat[tmp, ]
    x <- sub_dat2[, 1]
    y <- sub_dat2[, 2]
    plot(x, y, col = cluster_labels[tmp], asp = T, cex = 0.7, pch = 16,
         xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
         ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
         main = paste0("T.test p-value: ", round(t_matrix[i, j], 5),
                       "\n", cell_label[i], " and\n", cell_label[j]))
  }
}
```

## Method 2 : Classification Error (logistic regression)

```{r}
# Calculate classification errors of 7c2 pairs

accuracy <- matrix(NA, nrow = cell_num, ncol = cell_num)
sub_dat <- dat[, c(ind1, ind2)]
for (i in 2:cell_num){
  for (j in 1:(i-1)){
    tmp <- which(cluster_labels %in% c(i,j))
    cell_type2 <- cluster_labels[tmp]
    sub_dat2 <- sub_dat[tmp, ]
    dat_df <- data.frame(x1 = sub_dat2[,1], x2 = sub_dat2[,2],
                         label = as.factor(cell_type2))
    log_res <- stats::glm(label ~ x1 + x2 + 1,
                          data = dat_df, family = "binomial")
    predictions <- (stats::predict(log_res,
                                   newdata = dat_df, type = "response") > 0.5)
    conf_table <- table(cell_type2, predictions)
    accuracy[i, j] <- sum(diag(conf_table)) / sum(conf_table)
  }
}
```

```{r}
par(mfrow = c(3,4))
for (i in 2:cell_num){
  for (j in 1:(i-1)){
    tmp <- which(cluster_labels %in% c(i,j))
    sub_dat2 <- sub_dat[tmp, ]
    x <- sub_dat2[, 1]
    y <- sub_dat2[, 2]
    plot(x, y, col = cluster_labels[tmp], asp = T, cex = 0.7, pch = 16,
         xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
         ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
         main = paste0("Accuracy: ", round(accuracy[i, j], 3),
                       "\n", cell_label[i], " and\n", cell_label[j]))
  }
}
```

## Method 3 : Clustering Objective Compared to Random Assignment (K-means)

```{r}
.l2norm <- function(x){sqrt(sum(x^2))}

compute_ss <- function(dat, cluster_label){
 stopifnot(nrow(dat) == length(cluster_label))
 
 uniq_val <- unique(cluster_label)
 
 mean_list <- lapply(uniq_val, function(x){
  idx <- which(cluster_label == x)
  mean_vec <- colMeans(dat[idx,])
 })
 
 sum(sapply(1:nrow(dat), function(i){
  .l2norm(dat[i,] - mean_list[[which(uniq_val == cluster_label[i])]])
 }))
}

par(mfrow = c(3,2))
for (i in 2:cell_num){
  for (j in 1:(i-1)){
    tmp <- which(cluster_labels %in% c(i,j))
    cell_type2 <- cluster_labels[tmp]
    sub_dat2 <- sub_dat[tmp, ]
    
    set.seed(10)
    new_label <- sample(1:2, size = nrow(sub_dat2), replace = T)
    
    real_ss <- compute_ss(sub_dat2, cell_type2)
    random_ss <- compute_ss(sub_dat2, new_label)
    
    plot(sub_dat2[,1], sub_dat2[,2], cex = 0.7,
         asp = T, col = as.numeric(as.factor(cell_type2)), pch = 16,
         xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
         ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
         main = paste0("SS: ", real_ss,
                       "\n", cell_label[i], " and\n", cell_label[j]))
    plot(sub_dat2[,1], sub_dat2[,2], 
         asp = T, col = new_label, pch = 16, cex = 0.7,
         xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
         ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
         main = paste0("SS: ", random_ss, "\nwith Randomly Assignment",
                       "\nDifference : ", abs(random_ss - real_ss)))
  }
}
```

# Clustering Method (1 vs 6 cells)

## Method 1 : P-values in Two-sample Tests

```{r}
sub_dat <- dat[, c(ind1, ind2)]
pval_vec <- c()

# Conduct the t.test for 7C2 times 
for (i in 1:cell_num){
    x <- sub_dat[which(cluster_labels == i), ]
    y <- sub_dat[which(cluster_labels != i), ]
    
    ttest_xy <- stats::t.test(x, y, alternative = "two.sided")
    pval_vec <- c(pval_vec, ttest_xy$p.value)
}

```

```{r}
par(mfrow = c(2,4))
for (i in 1:cell_num){
  x <- sub_dat[which(cluster_labels == i), ]
  
  plot(sub_dat, asp = T, cex = 0.7, pch = 16,
       xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
       ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
       main = paste0(cell_label[i], "\nand the rest\n",
                     "T.test p-value: ", round(pval_vec[i], 5)))
  points(x, col = cluster_labels[i], pch = 16, asp = T)
}
```

## Method 2 : Classification Error (logistic regression)

```{r}
# Calculate classification errors 
accuracy_vec <- c()

for (i in 1:cell_num){
    binary_cell <- ifelse(cluster_labels == i, 1, 2)
    dat_df <- data.frame(x1 = sub_dat[,1], x2 = sub_dat[,2],
                         label = as.factor(binary_cell))
    log_res <- stats::glm(label ~ x1 + x2 + 1,
                          data = dat_df, family = "binomial")
    predictions <- (stats::predict(log_res,
                                   newdata = dat_df, type = "response") > 0.5)
    conf_table <- table(binary_cell, predictions)
    accuracy_vec <- c(accuracy_vec,
                  sum(diag(conf_table)) / sum(conf_table))
}
```

```{r}
par(mfrow = c(2,4))
for (i in 1:cell_num){
  x <- sub_dat[which(cluster_labels == i), ]
  plot(sub_dat, asp = T, cex = 0.7, pch = 16,
       xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
       ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
       main = paste0(cell_label[i], " and the rest\n",
                     "Accuracy: ", round(accuracy_vec[i], 3)))
  points(x, col = cluster_labels[i], pch = 16, asp = T)
}
```

## Method 3 : Clustering Objective Compared to Random Assignment (K-means)

```{r}
par(mfrow = c(3,2))
for (i in 1:cell_num){
  x <- sub_dat[which(cluster_labels == i), ]
  binary_cell <- ifelse(cluster_labels == i, 1, 2)
  
  set.seed(10)
  new_label <- sample(1:2, size = nrow(sub_dat), replace = T)
  y <- sub_dat[which(new_label == i), ]
  
  real_ss <- compute_ss(sub_dat, binary_cell)
  random_ss <- compute_ss(sub_dat, new_label)
  
  plot(sub_dat[,1], sub_dat[,2], cex = 0.7,
       asp = T, col = as.numeric(as.factor(binary_cell)), pch = 16,
       xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
       ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
       main = paste0(cell_label[i], " and the rest\n",
                     "SS: ", real_ss))
  
  plot(sub_dat[,1], sub_dat[,2], 
       asp = T, col = new_label, pch = 16, cex = 0.7,
       xlab = paste0(colnames(dat)[ind1], ", (", ind1, ")"),
       ylab = paste0(colnames(dat)[ind2], ", (", ind2, ")"),
       main = paste0("Randomly Assignment\n", "SS: ", random_ss, 
                     "\nDifference : ", abs(random_ss - real_ss)))
}
```

