---
title: "Preliminary_analysis"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document is a simple analysis to investigate the genes

# Setup

## Loading in data

```{r}
dat <- read.csv("../../data/esvd_preprocessed.csv", row.names = 1)
dat_raw <- read.csv("../../data/esvd_raw.csv", row.names = 1)
cell_type <- read.csv("../../data/esvd_cell_type.csv", row.names = 1)

dat[1:5,1:5]
dat_raw[1:5,1:5]
head(cell_type)

dim(dat)
dim(dat_raw)
dim(cell_type)
```

## Setting up colors

```{r}
cluster_labels <- as.numeric(as.factor(cell_type$cell_type))
table(cluster_labels)

color_func <- function(alpha = 0.2){
  c(rgb(240/255, 228/255, 66/255, alpha), #yellow
    rgb(86/255, 180/255, 233/255, alpha), #skyblue
    rgb(0/255, 158/255, 115/255, alpha), #bluish green
    rgb(0/255, 114/255, 178/255,alpha), #blue
    rgb(230/255, 159/255, 0/255,alpha), #orange
    rgb(100/255, 100/255, 100/255, alpha)) #gray
}
color_name_vec <- c("yellow", "skyblue", "bluish green", "blue", "orange", "gray")

num_order_vec_esvd <- c(5, rep(3,2), c(6,1,1,4,4,4), rep(2,2),  rep(5,2))
col_vec_esvd <- color_func(0.5)[num_order_vec_esvd]
col_name_esvd <- color_name_vec[num_order_vec_esvd]
order_vec_esvd <- c(3, 5.1, 5.2, seq(6.1, 6.6, by = 0.1), 4.1, 4.2, 2, 1)
col_info_esvd <- data.frame(name = levels(as.factor(cell_type$cell_type)),
                            idx = sort(unique(cluster_labels)),
                            order = order_vec_esvd,
                            col_name = col_name_esvd,
                            col_code = col_vec_esvd)
col_info_esvd$factor_idx <- as.numeric(as.factor(col_info_esvd$col_name))
col_info_esvd[,c(5,6)] <- col_info_esvd[,c(6,5)]
colnames(col_info_esvd)[c(5,6)] <- colnames(col_info_esvd)[c(6,5)]
col_info_esvd
```

# Analysis of raw dataset

## Plotting some scatter plots

```{r}
par(mfrow = c(2,2))
for(i in 1:4){
 set.seed(i)
 rand_vec <- sample(1:ncol(dat_raw), 2)
 idx1 <- rand_vec[1]; idx2 <- rand_vec[2]
 
 plot(dat_raw[,idx1], dat_raw[,idx2], col = col_info_esvd$col_code[cluster_labels], 
      pch = 16, xlab = paste0(colnames(dat_raw)[idx1], ", (", idx1, ")"),
      ylab = paste0(colnames(dat_raw)[idx2], ", (", idx2, ")"), asp = T)
}
```

```{r, cache = T}
cor_mat_raw <- stats::cor(dat_raw)
cor_mat_raw[upper.tri(cor_mat_raw, diag = T)] <- NA
cor_mat_raw[1:5,1:5]

# plot the smallest correlations
cor_vec_raw <- sort(abs(cor_mat_raw), decreasing = T)
plot(cor_vec_raw)
```

## Plotting scatterplots with high correlations

```{r}
#plot the high correlations
par(mfrow = c(2,2))
for(i in 1:4){
 idx <- which(abs(cor_mat_raw) == cor_vec_raw[i], arr.ind = T)
 idx1 <- idx[1]; idx2 <- idx[2]
 
 plot(dat_raw[,idx1], dat_raw[,idx2], col = col_info_esvd$col_code[cluster_labels], asp = T,
      pch = 16, xlab = paste0(colnames(dat_raw)[idx1], ", (", idx1, ")"),
      ylab = paste0(colnames(dat_raw)[idx2], ", (", idx2, ")"), 
      main = paste0("Correlation of ", round(cor_mat_raw[idx1, idx2], 3)))
}
```

## Plotting scatterplots with low correlations

```{r}
#plot the lowest correlations
par(mfrow = c(2,2))
for(i in 1:4){
 idx <- which(abs(cor_mat_raw) == rev(cor_vec_raw)[i], arr.ind = T)
 idx1 <- idx[1]; idx2 <- idx[2]
 
 plot(dat_raw[,idx1], dat_raw[,idx2], col = col_info_esvd$col_code[cluster_labels], asp = T,
      pch = 16, xlab = paste0(colnames(dat_raw)[idx1], ", (", idx1, ")"),
      ylab = paste0(colnames(dat_raw)[idx2], ", (", idx2, ")"), 
      main = paste0("Correlation of ", round(cor_mat_raw[idx1, idx2], 3)))
}
```

# Analysis of smoothed dataset

## Plotting some scatter plots

```{r}
par(mfrow = c(2,2))
for(i in 1:4){
 set.seed(i)
 rand_vec <- sample(1:ncol(dat), 2)
 idx1 <- rand_vec[1]; idx2 <- rand_vec[2]
 
 plot(dat[,idx1], dat[,idx2], col = col_info_esvd$col_code[cluster_labels], 
      pch = 16, xlab = paste0(colnames(dat)[idx1], ", (", idx1, ")"),
      ylab = paste0(colnames(dat)[idx2], ", (", idx2, ")"), asp = T)
}
```

```{r, cache = T}
cor_mat <- stats::cor(dat)
cor_mat[upper.tri(cor_mat, diag = T)] <- NA
cor_mat[1:5,1:5]

# plot the smallest correlations
cor_vec <- sort(abs(cor_mat), decreasing = T)
plot(cor_vec)
```

## Plotting scatterplots with high correlations

```{r}
#plot the high correlations
par(mfrow = c(2,2))
for(i in 1:4){
 idx <- which(abs(cor_mat) == cor_vec[i], arr.ind = T)
 idx1 <- idx[1]; idx2 <- idx[2]
 
 plot(dat[,idx1], dat[,idx2], col = col_info_esvd$col_code[cluster_labels], asp = T,
      pch = 16, xlab = paste0(colnames(dat)[idx1], ", (", idx1, ")"),
      ylab = paste0(colnames(dat)[idx2], ", (", idx2, ")"), 
      main = paste0("Correlation of ", round(cor_mat[idx1, idx2], 3)))
}
```

## Plotting scatterplots with low correlations

```{r}
#plot the lowest correlations
par(mfrow = c(2,2))
for(i in 1:4){
 idx <- which(abs(cor_mat) == rev(cor_vec)[i], arr.ind = T)
 idx1 <- idx[1]; idx2 <- idx[2]
 
 plot(dat[,idx1], dat[,idx2], col = col_info_esvd$col_code[cluster_labels], asp = T,
      pch = 16, xlab = paste0(colnames(dat)[idx1], ", (", idx1, ")"),
      ylab = paste0(colnames(dat)[idx2], ", (", idx2, ")"), 
      main = paste0("Correlation of ", round(cor_mat[idx1, idx2], 3)))
}
```
